---
title: "STATS 101A HW1"
author: "Prisha Chowdhury"
date: "2026-01-06"
output: html_document
---
#problem 1 
1. D. Strong positive linear Relation
2. slope = 8870.89
 as you have one more year of experience increasing it is going to increase by avg 
3. B) 86% of the total variability in salary is explained by the model.
4. C 
5. 
Q3.(0.93^2)
C 

Q4) y- y hat = residual plot , C: no problem 

Q5) Outside of the range of my data point 
b = y bar- a(x) plug in 
101904.47

##problem 2 
1)

$$H_0:\mu = 2.5  \\ H1:\mu > 2.5 $$
2)$$T=\frac{2.9 - 2.5 }{\frac{1.2} }= 2.357$$
```{r}
1- pt(2.357,df = 49 )
```
3) p value = 0.01123
4) rejecting the null, there is sufficient evidence, more than 2.5 hours 
5) 

```{r}
qt ( 0.975, df = 49 )
```
$$2.9\pm2.01$$
```{r}
```

11:36am 
its between thes bounds, 95% confident that this is true 

##problem 3 
download the heart.csv 
```{r}
heart <-read.csv("Heart.csv")
model <- lm(MaxHR ~ Age ,data = heart)
summary(model)
```
$$\hat{MaxHR} = -0.9966 * Age + 203.8634$$
average 

```{r}
plot(MaxHR ~ Age ,data = heart)
abline(model, col = "red")
```

3)R square:  0.1552, total variability, not that good 
plot residual 
```{r}
plot(model$residuals~heart$Age)
```

